Computer Science House Constitution

### 2021-09-21 constitution.tex
Better wording on "extend the payment"
Co-authored-by: Harlan Haskins <harlan@apple.com>
allow honorary and advisory members accounts without completion of packet
Added Polygamy/Polyamory Directorship
Removes spending committees, redifines limits on directorships using their budgets

\asubsubsection{Expenditure Approval}
All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
Single expenditures may not exceed seventy-five dollars (\$75) and total expenditures may not exceed one-hundred dollars (\$100).
A total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars (\$100), but not to exceed three-hundred dollars (\$300).
A quorum of one-quarter the number of current active members is required for the meeting to take place and for any vote to be considered valid, it must be passed by a simple two-thirds majority.
\\*\\*
For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
This proposal includes the project budget, inventory of required resources, and a timeline for completion.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.

>>>>

\asubsubsection{Expenditure Approval}
All House expenditures must be approved by both the Financial Director and the appropriate Director (from whose budget the funds will be drawn).
Single expenditures may not exceed five percent of a directorship's budget (5\%) and total expenditures may not exceed ten percent (10\%).
A single expenditure is defined as one line item on a receipt, and a total expenditure is defined as all the funds drawn for a specific event, project, piece of equipment, or service.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by a Simple Majority vote at House meeting before the funds may be appropriated, as defined in \ref{Simple Majority}.
\\*\\*
For expenditures exceeding \$300 in total funding, a Complete Project Proposal must be presented to House at a House meeting.
This proposal includes the project budget, inventory of required resources, and a timeline for completion.
\\* \\*
If an appropriate Directorship cannot be determined for an expenditure, it is to be brought up for approval at House meeting as a Miscellaneous expenditure and approved by a simple majority vote, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
\\* \\*
Funds allocated for a project not spent by the end of the Standard Operating Session \ref{Standard Operating Session} in which they were approved are voided, unless otherwise specified during the original voting process.
